---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyr)
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(stringr)
```


```{r}
micro<-read_excel('./data/eMIC Notebook - Berg.xlsx', col_types = c('Site_location' = 'text')) %>% 
  fill(`MID Number`, .direction = "down") %>% 
  fill(`Colony Morphology`, .direction = "down") %>% 
  fill(`Performance Date`, .direction = "down") %>% 
  pivot_longer(cols = starts_with('Site Location'), values_drop_na = TRUE) %>% 
  dplyr::select(`Performance Date`, `MID Number`, `Colony Morphology`, value) %>% 
  rename(date = `Performance Date`, ID = `MID Number`, sample_site = value) %>% 
  mutate(date = parse_date_time(`date`,orders = 'd%B%Y%')) %>% 
  mutate(Q = quarter(`date`, with_year = TRUE))
```
Possible variation on a sample site name (Human Data Entry Error)
311-5: Air 5
311:5: Air 5
311-5:Air 5
311-5 
311-5 Air 5
311-5:Air5
311: 5Air 5
311-5 :Air 5
311-5Air 5
311-5: air 5
311-5Air5
Construct a Regex that matches all of these and a match that converts to 311-5


```{r}
micro$sample_site<-micro$sample_site %>% 
  str_trunc(.,6, ellipsis = '',side = c('right')) %>% 
  str_replace('Air', '') %>% 
  str_replace('-\\s+', '-') %>% 
  str_squish %>% 
  str_replace('-$', '') %>% 
  str_replace('^[A-Za-z]+[\\s?|\\S?].[A-Za-z]*\\W\\d?\\W?|^0\\d+\\S\\w|\\d+mL|\\d% Cre', '') %>% 
  str_replace('^[A-Za-z]+', '') %>%
  str_replace('P|Run|[$]|10 mL|Dil|-Bac|-Fin|-che|-Che|\\d-Mi|-Sle|1-Lab|<62> T|-bac', '') %>% 
  str_replace('^[-]', '') %>% 
  str_replace(' ', '') %>% 
  str_replace('108-\\d*\\w*|110-\\d*\\w*', "")

micro$sample_site[micro$sample_site==""]<-NA

micro<- micro %>% drop_na()
```

```{r}
micro %>% write_csv('./data/micro.csv')
```

```{r}
micro2<-read_csv('./data/micro.csv')
```


```{r}
sample_site<-micro$sample_site %>%
  unique() %>% 
  tibble()

sample_site %>% write_excel_csv('./data/sample_sites.csv')
```


MFG-Ca
NB-Fin
CDB-Pa
MFG-Ra
TSA Se
swab s
C2-Mic
50mL
10mL
MWP-Ba
CDB-(2
CDB-
TSA SI
DAS(F)
BW(F)-
0162-F
3% Cre
DS-Che
Rack 2
PB Dil
EC Run
Movab
PA Run

```{r}
#Count ID grouped by site and add in Time component with date column.
micro %>% 
  group_by(sample_site) %>% 
  summarise(tot_ids = n()) %>% 
  ungroup() %>% 
  arrange(desc(tot_ids))
```

```{r}
quarters<-micro %>% 
  group_by(sample_site, Q) %>% 
  summarise(tot_ids = n()) %>% 
  ungroup() %>% 
  arrange(desc(tot_ids))
```

```{r}
ggplot(quarters, aes(x = Q, y = tot_ids, color = sample_site, )) +
  geom_col(show.legend = FALSE)
```
```{r}
dates<-micro %>% 
  group_by(sample_site, date) %>% 
  summarise(tot_ids = n()) %>% 
  ungroup() %>% 
  arrange(desc(tot_ids))
```


```{r}
df <- quarters %>% filter(str_detect(sample_site, "^302"))
```

```{r}
t<-ggplot(df, aes(x = Q, y = tot_ids, color = sample_site)) +
  geom_col()
```

```{r}
t + facet_wrap(vars(sample_site))
```


```{r}
df <- dates %>% filter(str_detect(sample_site, "302-1"))
```

```{r}
t<-ggplot(df, aes(x = date, y = tot_ids, color = sample_site)) +
  geom_col()
```

```{r}
graph<-t + facet_wrap(vars(sample_site))
```
Show me sites that are increasing in counts for a particular year. to select for remediation

